---
title: "2026_insecticideusage_lasso_threeway"
output: html_document
date: "2026-03-18"
---

```{r}
library(tidyverse)
library(DHARMa)
library(performance)
library(glmmLasso)
library(lme4)
library(sjPlot)
library(car)
library(glmmTMB)
library(caret)
```

#Load and clean data
```{r}
df <- read.csv("2026_insecticideanalyses_upload_csv.csv")%>% 
  dplyr::select(-Area2025cia, -ftITN, -sum_ITN, -sum_RS, -sum_SS, -sum_LA, -newITN) %>% 
  rename(Malaria = Malaria_rate, Dengue = Dengue_rate) %>% 
  filter(mean_temp > -200) #Removing island locations that were not covered by ERA5 climate datasets
df$Pop = as.numeric(df$Pop)

df2 <- df %>% 
  dplyr::select(Country, newsum, Dengue, Malaria, mean_temp, mean_precip, hdi, Pop, TotalPop, Year) %>% 
  drop_na() %>% 
  droplevels()

df2$sum_2 <- df2$newsum 

df2$Country = as.factor(df2$Country)
df2$Y = log(df2$sum_2 + 0.001)

#Create a transformed response variable to represent the offset for the lasso selection as glmmlasso does not take offsets
df2$Y2 = log((df2$sum_2+0.001)/df2$TotalPop)


#ln(x+1) transform the overdispersed predictor variables
df2$Malaria <- log1p(df2$Malaria)
df2$Dengue <- log1p(df2$Dengue)
df2$mean_precip <- log1p(df2$mean_precip)
df2$Pop <- log1p(df2$Pop)

#log transform population for the offset
df2$logTotalPop <- log(df2$TotalPop)

df3 <- df2
df2[,c(3:8)] <- scale(df2[,c(3:8)])


df2 <- data.frame(df2)

family = gaussian(link = 'identity')

cov(df2[,c(3:8)])
```
#Testing the polynomial terms for temperature and precipitation
```{r}

z <- glmmTMB(log(sum_2 + 0.001) ~ (Malaria + Dengue + mean_temp + mean_precip + hdi + Pop)^3 + (1|Country) + offset(log(TotalPop)), data = df2, family = family)

x <- glmmTMB(Y~ (Malaria + Dengue + poly(mean_temp, 2) + mean_precip + hdi + Pop)^3 + (1|Country)+ offset(logTotalPop), data = df2, family = family)
y <- glmmTMB(Y~ (Malaria + Dengue + mean_temp + poly(mean_precip, 2) + hdi + Pop)^3 + (1|Country)+ offset(logTotalPop), data = df2, family = family)

BIC( z, x, y)
```

Checking on the lowest lambda value that shrinks all coefficients to 0, which will be
used as the maximum lambda value in the lasso process.
```{r}
m <- glmmLasso(Y2~ (Malaria + Dengue + mean_temp + mean_precip + hdi + Pop)^3, rnd = list(Country=~1), 
                            family = family, data = df2, lambda=1165, switch.NR = TRUE, final.re = TRUE) 

summary(m)

```
#Max lambda is 1165

Lasso using cross validation to select the optimal lambda
```{r}
set.seed(1009)
N<-dim(df2)[1]
ind<-sample(N,N)
lambda <- lambda <- exp(seq(log(1165), log(1165 * .0001), length.out = 200)) #The lambda values tested

kk<-5
nk <- floor(N/kk)

Devianz_ma<-matrix(Inf,ncol=kk,nrow=length(lambda))

#Starting model
library(MASS);library(nlme)
PQL <- glmmPQL(Y2~ 1,random = ~1|Country,family=family,data=df2)

Delta.start <- as.matrix(t(c(as.numeric(PQL$coef$fixed),rep(0,41),as.numeric(t(PQL$coef$random$Country)))))
Q.start <- as.numeric(VarCorr(PQL)[1,1])


#Loop through each k-fold 
for (i in 1:kk)
{
  print(paste("CV Loop ", i,sep=""))
  
    if (i < kk)
    {
      indi <- ind[(i-1)*nk+(1:nk)]
    }else{
      indi <- ind[((i-1)*nk+1):N]
    }
    
    df2.train<-df2[-indi,]
    df2.test<-df2[indi,]
    
    Delta.start.loop <- Delta.start
    Q.start.loop <- Q.start
    
    ## loop over lambda grid
    for(j in 1:length(lambda))
    {
      glm4 <- try(glmmLasso(Y2~(Malaria + Dengue + mean_temp + mean_precip + hdi + Pop)^3, rnd = list(Country=~1),  
                            family = family, data = df2.train, lambda=lambda[j], switch.NR=TRUE, final.re=TRUE,
                            control=list(start=Delta.start.loop, q_start=Q.start.loop)),
                  silent=TRUE) 
      
      if(!inherits(glm4, "try-error"))
      {  
        y.hat <- predict(glm4, df2.test)
        
        
        Delta.start.loop <- glm4$Deltamatrix[glm4$conv.step,]
        Q.start.loop <- glm4$Q_long[[glm4$conv.step+1]]
        
        Devianz_ma[j,i] <- sum(family$dev.resids(df2.test$Y2, y.hat, wt=rep(1, length(y.hat)))) 
      }
    }
}

Devianz_vec<-apply(Devianz_ma,1,sum)
opt4<-which.min(Devianz_vec)

#Fit full model until the optimal lambda
for(j in 1:opt4)
{  
glm4.big <- glmmLasso(Y2~(Malaria + Dengue + mean_temp + mean_precip + hdi + Pop)^3, rnd = list(Country=~1),  
                        family = family, data = df2, lambda=lambda[j],switch.NR=TRUE,final.re=TRUE,
                        control=list(start=Delta.start[j,],q_start=Q.start[j]))
Delta.start<-rbind(Delta.start,glm4.big$Deltamatrix[glm4.big$conv.step,])
Q.start<-c(Q.start,glm4.big$Q_long[[glm4.big$conv.step+1]])
}

glm4_final <- glm4.big

```

```{r}
plot(lambda, Devianz_vec,
     type = "b", 
     xlab = "Lambda",
     ylab = "Cross-Validated Deviance",
     main = "Overall Model Lambda Selection",
     log = "x"
)

opt4_lambda <- lambda[opt4]
points(opt4_lambda, Devianz_vec[opt4], col = "red", pch = 19, cex = 1.5)
abline(v = opt4_lambda, col = "red", lty = 2)
text(opt4_lambda, min(Devianz_vec), paste("Optimal Lambda:", round(opt4_lambda, 3)),
     pos = 4, col = "red")

```
The optimal lambda is 7.166

Plot this model
```{r}
selected_fixed_effects <- names(glm4_final$coefficients[glm4_final$coefficients != 0])
selected_fixed_effects <- selected_fixed_effects[-1]
fixed_formula_selected <- as.formula(paste("Y2 ~", paste(selected_fixed_effects, collapse = " + "), "+ (1|Country)"))


model_refit <- glmmTMB(log(sum_2 + 0.001) ~ Malaria + Dengue + mean_temp + hdi + Pop + Malaria*Dengue + 
    Malaria*mean_temp + Malaria*mean_precip + Malaria*hdi + Malaria*Pop + 
    Dengue*mean_temp + Dengue*hdi + Dengue*Pop + mean_temp*mean_precip + 
    mean_temp*hdi + mean_temp*Pop + mean_precip*hdi + hdi*Pop + 
    Malaria*Dengue*mean_precip + Malaria*Dengue*Pop + Malaria*mean_temp*mean_precip + 
    Malaria*mean_temp*hdi + Malaria*mean_temp*Pop + Malaria*mean_precip*hdi + 
    Malaria*mean_precip*Pop + Malaria*hdi*Pop + Dengue*mean_temp*mean_precip + 
    Dengue*mean_temp*hdi + Dengue*mean_temp*Pop + Dengue*mean_precip*hdi + 
    Dengue*mean_precip*Pop + Dengue*hdi*Pop + mean_temp*mean_precip*hdi + 
    mean_temp*mean_precip*Pop + mean_temp*hdi*Pop + mean_precip*hdi*Pop + 
    (1 | Country) + offset(log(TotalPop)), data = df2, family = family)




summary(model_refit)



car::Anova(model_refit, type = "III")

resid <- DHARMa::simulateResiduals(model_refit, n = 1000)
testResiduals(resid)
DHARMa::plotResiduals(resid)

```


Repeated k-folds CV within country:
```{r}
library(rsample)
library(glmmTMB)
library(performance)
library(caret)

k <- 5
n_repeats <- 50
all_repeats_results <- list()

for (r in 1:n_repeats) {
  set.seed(19768876 + r)
  folds <- createFolds(df2$Country, k = k)
  cv_results <- list()
  for (i in 1:k) {
    indi <- folds[[i]]
    test_data <- df2[-indi,]
    train_data <- df2[indi,]
    
    model_cv <- glmmTMB(
      log(sum_2 + 0.001) ~ Malaria + Dengue + mean_temp + hdi + Pop + Malaria*Dengue + 
    Malaria*mean_temp + Malaria*mean_precip + Malaria*hdi + Malaria*Pop + 
    Dengue*mean_temp + Dengue*hdi + Dengue*Pop + mean_temp*mean_precip + 
    mean_temp*hdi + mean_temp*Pop + mean_precip*hdi + hdi*Pop + 
    Malaria*Dengue*mean_precip + Malaria*Dengue*Pop + Malaria*mean_temp*mean_precip + 
    Malaria*mean_temp*hdi + Malaria*mean_temp*Pop + Malaria*mean_precip*hdi + 
    Malaria*mean_precip*Pop + Malaria*hdi*Pop + Dengue*mean_temp*mean_precip + 
    Dengue*mean_temp*hdi + Dengue*mean_temp*Pop + Dengue*mean_precip*hdi + 
    Dengue*mean_precip*Pop + Dengue*hdi*Pop + mean_temp*mean_precip*hdi + 
    mean_temp*mean_precip*Pop + mean_temp*hdi*Pop + mean_precip*hdi*Pop + 
    (1 | Country) + offset(log(TotalPop)),
      family = family,
      data = train_data)

    test_pred <- predict(model_cv, newdata = test_data, type = "response", allow.new.levels = TRUE)
    train_pred <- predict(model_cv, newdata = train_data, type = "response", re.form = NA)
    train_pred_c <- predict(model_cv, newdata = train_data, type = "response")
    
    test_obs <- test_data$Y
  train_obs <- train_data$Y
    
    test_r2 <- cor(test_pred, test_obs, use = "complete.obs")^2
    train_r2 <- cor(train_pred, train_obs, use = "complete.obs")^2
    train_r2_c <- cor(train_pred_c, train_obs, use = "complete.obs")^2
    
    cv_results[[i]] <- data.frame(
      Repeat = r,
      Fold = i,
      Test_R2 = as.numeric(test_r2),
      Train_R2 = as.numeric(train_r2),
      Train_R2_Cond = as.numeric(train_r2_c)
    )
  }
  
  all_repeats_results[[r]] <- do.call(rbind, cv_results)
}

final_summary <- do.call(rbind, all_repeats_results)

library(dplyr)
grand_summary <- final_summary %>%
  summarise(
    Mean_Test_R2 = mean(Test_R2, na.rm = TRUE),
    SD_Test_R2 = sd(Test_R2, na.rm = TRUE),
    Mean_Train_R2 = mean(Train_R2, na.rm = TRUE),
    Mean_Train_R2_Cond = mean(Train_R2_Cond, na.rm = TRUE)
  )

print(grand_summary)
```

Repeated k-folds CV with LOO approach for countries:
```{r}
library(rsample)
library(glmmTMB)
library(performance)
library(caret) 

k <- 10
n_repeats <- 50
all_repeats_results <- list()

for (r in 1:n_repeats) {
  set.seed(19768876 + r)
  folds <- groupKFold(df2$Country, k = k)
  cv_results <- list()

  for (i in 1:k) {
    indi <- folds[[i]]
    test_data <- df2[-indi,]
    train_data <- df2[indi,]
    
    model_cv <- glmmTMB(
      log(sum_2 + 0.001) ~ Malaria + Dengue + mean_temp + hdi + Pop + Malaria*Dengue + 
    Malaria*mean_temp + Malaria*mean_precip + Malaria*hdi + Malaria*Pop + 
    Dengue*mean_temp + Dengue*hdi + Dengue*Pop + mean_temp*mean_precip + 
    mean_temp*hdi + mean_temp*Pop + mean_precip*hdi + hdi*Pop + 
    Malaria*Dengue*mean_precip + Malaria*Dengue*Pop + Malaria*mean_temp*mean_precip + 
    Malaria*mean_temp*hdi + Malaria*mean_temp*Pop + Malaria*mean_precip*hdi + 
    Malaria*mean_precip*Pop + Malaria*hdi*Pop + Dengue*mean_temp*mean_precip + 
    Dengue*mean_temp*hdi + Dengue*mean_temp*Pop + Dengue*mean_precip*hdi + 
    Dengue*mean_precip*Pop + Dengue*hdi*Pop + mean_temp*mean_precip*hdi + 
    mean_temp*mean_precip*Pop + mean_temp*hdi*Pop + mean_precip*hdi*Pop + 
    (1 | Country) + offset(log(TotalPop)),
      family = family,
      data = train_data)

    test_pred <- predict(model_cv, newdata = test_data, type = "response", allow.new.levels = TRUE)
    train_pred <- predict(model_cv, newdata = train_data, type = "response", re.form = NA)
    train_pred_c <- predict(model_cv, newdata = train_data, type = "response")
    
    test_obs <- log(test_data$sum_2 + 0.001)
  train_obs <- log(train_data$sum_2 + 0.001)
    
    test_r2 <- cor(test_pred, test_obs, use = "complete.obs")^2
    train_r2 <- cor(train_pred, train_obs, use = "complete.obs")^2
    train_r2_c <- cor(train_pred_c, train_obs, use = "complete.obs")^2
    
    cv_results[[i]] <- data.frame(
      Repeat = r,
      Fold = i,
      Test_R2 = as.numeric(test_r2),
      Train_R2 = as.numeric(train_r2),
      Train_R2_Cond = as.numeric(train_r2_c)
    )
  }
  
  all_repeats_results[[r]] <- do.call(rbind, cv_results)
}

final_summary <- do.call(rbind, all_repeats_results)

library(dplyr)
grand_summary <- final_summary %>%
  summarise(
    Mean_Test_R2 = mean(Test_R2, na.rm = TRUE),
    SD_Test_R2 = sd(Test_R2, na.rm = TRUE),
    Mean_Train_R2 = mean(Train_R2, na.rm = TRUE),
    SD_Train_R2 = sd(Train_R2, na.rm = TRUE),
    Mean_Train_Conditional = mean(Train_R2_Cond, na.rm = TRUE)
  )

print(grand_summary)
```


Determine the singificant effects using a type III ANOVA:
```{r}
car::Anova(model_refit, type = "III")

```

Refitting the model with the scale wraparound so sjPlot knows units:
```{r}
model_refit <- glmmTMB(Y ~ 
scale(Malaria) + scale(Dengue) + scale(mean_temp) + scale(hdi) + scale(Pop) + scale(Malaria)*scale(Dengue) + 
    scale(Malaria)*scale(mean_temp) + scale(Malaria)*scale(mean_precip) + scale(Malaria)*scale(hdi) + scale(Malaria)*scale(Pop) + 
    scale(Dengue)*scale(mean_temp) + scale(Dengue)*scale(hdi) + scale(Dengue)*scale(Pop) + scale(mean_temp)*scale(mean_precip) + 
    scale(mean_temp)*scale(hdi) + scale(mean_temp)*scale(Pop) + scale(mean_precip)*scale(hdi) + scale(hdi)*scale(Pop) + 
    scale(Malaria)*scale(Dengue)*scale(mean_precip) + scale(Malaria)*scale(Dengue)*scale(Pop) + scale(Malaria)*scale(mean_temp)*scale(mean_precip) + 
    scale(Malaria)*scale(mean_temp)*scale(hdi) + scale(Malaria)*scale(mean_temp)*scale(Pop) + scale(Malaria)*scale(mean_precip)*scale(hdi) + 
    scale(Malaria)*scale(mean_precip)*scale(Pop) + scale(Malaria)*scale(hdi)*scale(Pop) + scale(Dengue)*scale(mean_temp)*scale(mean_precip) + 
    scale(Dengue)*scale(mean_temp)*scale(hdi) + scale(Dengue)*scale(mean_temp)*scale(Pop) + scale(Dengue)*scale(mean_precip)*scale(hdi) + 
    scale(Dengue)*scale(mean_precip)*scale(Pop) + scale(Dengue)*scale(hdi)*scale(Pop) + scale(mean_temp)*scale(mean_precip)*scale(hdi) + 
    scale(mean_temp)*scale(mean_precip)*scale(Pop) + scale(mean_temp)*scale(hdi)*scale(Pop) + scale(mean_precip)*scale(hdi)*scale(Pop) + 
    (1 | Country) + offset(logTotalPop), data = df3, family = family)

summary(model_refit)
Anova(model_refit, type = "III")
```

scale(Malaria) already in
scale(hdi) already in

scale(Malaria):scale(Dengue) Replace the three way in paper, NEED TO ADD
scale(Malaria):scale(mean_temp) already in three way
scale(Malaria):scale(hdi) Already in, same pattern
scale(Malaria):scale(Pop) included in three way

scale(Malaria):scale(mean_temp):scale(Pop) Already in, same pattern
scale(Malaria):scale(Pop):scale(mean_precip) NEED TO ADD
scale(mean_temp):scale(Pop):scale(mean_precip) Already (main and supp)
scale(mean_temp):scale(hdi):scale(Pop) Already in, same pattern


Malaria*Dengue*Temp removed

Plots:
```{r}
panel1 <- plot_model(model_refit, type = "pred", terms = c("Malaria",  "hdi [.49,.63, .76]")) 

panel1 <- as.data.frame(panel1$data) %>% 
  rename("Malaria" = "x") %>% 
  rename("hdi" = "group")%>%
  mutate(predicted = if_else(predicted < -6.907755, -6.907755, predicted)) %>% 
  mutate(conf.low = if_else(conf.low < -6.907755, -6.907755, conf.low)) 
panel_a_1 <- ggplot(data = panel1, aes(x = Malaria, y = predicted, color = hdi))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = hdi), 
              alpha = 0.2, 
              color = NA)+
  geom_line(linewidth = 1) + 
  scale_color_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_fill_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_x_continuous(n.breaks = 4,
  labels = function(x) {
    val <- round(((exp(x) - 1) / 1000), 2)
    paste0(val, "k")
  }
)+
  scale_y_continuous(n.breaks = 6,
  labels = function(x) {
    val <- round(((exp(x) - .001) / 1000), 1)
    paste0(val, "k")
  }
)+
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(
    x = "AnBD Incidence (per 100k people)",
    y = expression(paste("Insecticide Use (SSC ",km^2,")")),
    color = "HDI",
    fill = "HDI"
  )


panel6 <- plot_model(model_refit, type = "pred", terms = c("Malaria",  "Pop", "mean_temp [16.4, 27.4]")) 
temp_labels <- c(
  "mean_temp = 16.4" = "Low Temperature",
  "mean_temp = 27.4" = "High Temperature"
)

panel6 <- as.data.frame(panel6$data) %>% 
  rename("Malaria" = "x") %>% 
  rename("Pop" = "group")%>%
  mutate(predicted = if_else(predicted < -6.907755, -6.907755, predicted)) %>% 
  mutate(conf.low = if_else(conf.low < -6.907755, -6.907755, conf.low)) 
panel_a_6 <- ggplot(data = panel6, aes(x = Malaria, y = predicted, color = Pop))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = Pop), 
              alpha = 0.2, 
              color = NA)+
  geom_line(linewidth = 1) + 
  scale_color_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_fill_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  facet_wrap(~facet, labeller = as_labeller(temp_labels))+
  scale_x_continuous(n.breaks = 4,
  labels = function(x) {
    val <- round(((exp(x) - 1) / 1000), 2)
    paste0(val, "k")
  }
)+
  scale_y_continuous(n.breaks = 6,
  labels = function(x) {
    val <- round(((exp(x) - .001) / 1000), 1)
    paste0(val, "k")
  }
)+
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(
    x = "AnBD Incidence (per 100k people)",
    y = expression(paste("Insecticide Use (SSC ",km^2,")")),
    color = "Population\nDensity",
    fill = "Population\nDensity"
  )

panel7 <- plot_model(model_refit, type = "pred", terms = c("Malaria",  "Dengue")) 
panel7 <- as.data.frame(panel7$data) %>% 
  rename("Malaria" = "x") %>% 
  rename("Dengue" = "group")%>%
  mutate(predicted = if_else(predicted < -6.907755, -6.907755, predicted)) %>% 
  mutate(conf.low = if_else(conf.low < -6.907755, -6.907755, conf.low))  
panel_a_7 <- ggplot(data = panel7, aes(x = Malaria, y = predicted, color = Dengue))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = Dengue), 
              alpha = 0.2, 
              color = NA)+
  geom_line(linewidth = 1) + 
  scale_color_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_fill_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_y_continuous(n.breaks = 6,
  labels = function(x) {
    val <- round(((exp(x) - .001) / 1000), 1)
    paste0(val, "k")
  }
)+
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(
    x = "AnBD Incidence (per 100k people)",
    y = expression(paste("Insecticide Use (SSC ",km^2,")")),
    color = "AeBD\nIncidence\n(per 100k\npeople)",
    fill = "AeBD\nIncidence\n(per 100k\npeople)"
  )



panel8 <- plot_model(model_refit, type = "pred", terms = c("mean_temp", "mean_precip"))
panel8 <- as.data.frame(panel8$data) %>% 
  rename("mean_precip" = "group")%>%
  mutate(predicted = if_else(predicted < -6.907755, -6.907755, predicted)) %>% 
  mutate(conf.low = if_else(conf.low < -6.907755, -6.907755, conf.low))  

panel_a_8 <- ggplot(data = panel8, aes(x = x, y = predicted, color = mean_precip))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = mean_precip), 
              alpha = 0.2, 
              color = NA)+
  geom_line(linewidth = 1) + 
  scale_color_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_fill_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_y_continuous(n.breaks = 6,
  labels = function(x) {
    val <- round(((exp(x) - .001) / 1000), 1)
    paste0(val, "k")
  })+
  theme_minimal() +
  theme(strip.text = element_text(size = 14),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(
    x = "Temperature (°C)",
    y = expression(paste("Insecticide Use (SSC ",km^2,")")),
    color = "Precipitation\n(m)",
    fill = "Precipitation\n(m)"
  )


panel9 <- plot_model(model_refit, type = "pred", terms = c("hdi",  "Pop", "mean_temp [16.4, 27.4]")) 
temp_labels <- c(
  "mean_temp = 16.4" = "Low Temperature",
  "mean_temp = 27.4" = "High Temperature"
)
panel9 <- as.data.frame(panel9$data) %>% 
  rename("hdi" = "x") %>% 
  rename("Pop" = "group")%>%
  mutate(predicted = if_else(predicted < -6.907755, -6.907755, predicted)) %>% 
  mutate(conf.low = if_else(conf.low < -6.907755, -6.907755, conf.low))  
panel_a_9 <- ggplot(data = panel9, aes(x = hdi, y = predicted, color = Pop))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = Pop), 
              alpha = 0.2, 
              color = NA)+
  geom_line(linewidth = 1) + 
  scale_color_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_fill_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  facet_wrap(~facet, labeller = as_labeller(temp_labels))+
  scale_y_continuous(n.breaks = 6,
  labels = function(x) {
    val <- round(((exp(x) - .001) / 1000), 1)
    paste0(val, "k")
  }
)+
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(
    x = "HDI",
    y = expression(paste("Insecticide Use (SSC ",km^2,")")),
    color = "Population\nDensity",
    fill = "Population\nDensity"
  )

panel2 <- plot_model(model_refit, type = "pred", terms = c("Malaria",  "Pop", "mean_precip [0.03, 0.17]")) 
precip_labels <- c(
  "mean_precip = 0.03" = "Low Precipitation",
  "mean_precip = 0.17" = "High Precipitation"
)
panel2 <- as.data.frame(panel2$data) %>% 
  rename("Malaria" = "x") %>% 
  rename("Pop" = "group")%>%
  mutate(predicted = if_else(predicted < -6.907755, -6.907755, predicted)) %>% 
  mutate(conf.low = if_else(conf.low < -6.907755, -6.907755, conf.low))  
panel_a_2 <- ggplot(data = panel2, aes(x = Malaria, y = predicted, color = Pop))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = Pop), 
              alpha = 0.2, 
              color = NA)+
  geom_line(linewidth = 1) + 
  scale_color_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_fill_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  facet_wrap(~facet, labeller = as_labeller(precip_labels))+
  scale_x_continuous(n.breaks = 4,
  labels = function(x) {
    val <- round(((exp(x) - 1) / 1000), 2)
    paste0(val, "k")
  }
)+
  scale_y_continuous(n.breaks = 6,
  labels = function(x) {
    val <- round(((exp(x) - .001) / 1000), 1)
    paste0(val, "k")
  }
)+
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(
    x = "AnBD Incidence (per 100k people)",
    y = expression(paste("Insecticide Use (SSC ",km^2,")")),
    color = "Population\nDensity",
    fill = "Population\nDensity"
  )



row_d_e <- cowplot::plot_grid(
  panel_a_8, panel_a_7, panel_a_1,
  ncol = 2,
  n_row = 2,
  align = "hv", 
  labels = c("A", "B", "C"), 
  rel_widths = c(1, 1) 
)


make_narrow <- function(plt, lbl) {
  cowplot::plot_grid(
    NULL, plt, NULL, 
    ncol = 3, 
    rel_widths = c(0, 0.8, 0.2),
    labels = c("", lbl, "")
  )
}

row_a <- make_narrow(panel_a_2, "E")
row_b <- make_narrow(panel_a_9, "F")
row_c <- make_narrow(panel_a_6, "D")

final_plot <- cowplot::plot_grid(
  row_d_e, row_c, row_a, row_b, 
  ncol = 1, 
  align = 'v', 
  rel_heights = c(2.5, 1.1, 1.1, 1.1)
)


cowplot::ggsave2(
  filename = "overallfigures_new.png",
  plot = final_plot,
  width = 10,
  height =13,
  units = "in",
  dpi = 1000
)



```


Supplemental figure
```{r}
panel3 <- plot_model(model_refit, type = "pred", terms = c("mean_temp", "mean_precip", "Pop [2.91, 5.48]"))
pop_labels <- c(
  "Pop = 2.91" = "Low Population Density",
  "Pop = 5.48" = "High Population Density"
)

panel3 <- as.data.frame(panel3$data) %>% 
  rename("mean_precip" = "group") %>% 
  mutate(predicted = if_else(predicted < 0, 0, predicted)) %>% 
  mutate(conf.low = if_else(conf.low < 0, 0, conf.low)) 

panel_a_3 <- ggplot(data = panel3, aes(x = x, y = predicted, color = mean_precip))+
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high, fill = mean_precip), 
              alpha = 0.2, 
              color = NA)+
  geom_line(linewidth = 1) + 
  scale_color_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
  scale_fill_brewer(palette = "Set2",labels = c("Low", "Average", "High"), guide = guide_legend(reverse = TRUE))+
    facet_wrap(~facet, labeller = as_labeller(pop_labels))+
  scale_y_continuous(n.breaks = 6,
  labels = function(x) {
    val <- round(((exp(x) - .001) / 1000), 1)
    paste0(val, "k")
  })+
  theme_minimal() +
  theme(strip.text = element_text(size = 14),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(), axis.line = element_line(colour = "black"))+
  labs(
    x = "Temperature (°C)",
    y = expression(paste("Insecticide Use (SSC ",km^2,")")),
    color = "Precipitation\n(m)",
    fill = "Precipitation\n(m)"
  )


cowplot::ggsave2(
  filename = "overallfigures_newsupp.png",
  plot = panel_a_3,
  width = 8,
  height =4,
  units = "in",
  dpi = 1000
)

```